---
title: "Food Accessibility and COVID-19 Cases in Washington"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
source('map.R')
```
---
Introduction:
Food accessibility has become a major concern for people during the pandemic,
even more so than ever before. Due to rising unemployment and public regulation
policies, the stability people may have experienced previously with food has
undoubtedly changed. We wanted to investigate the relationship between COVID-19,
the number of operating restaurants, and emergency food resources, to discover
how much of an effect the pandemic has had on people’s ability to access food,
specifically in King County. This will give us a better understanding of the
situation, which can help both our own communities as well as others moving forward.

```{r echo = F}
positives_map
```

The municipality in King County with the highest concentration of COVID
cases seems to be the city of Seattle. This is to be expected as Seattle's
population is significantly larger than the surrounding municipalities.
