---
title: "Food Accessibility and COVID-19 Cases in Washington"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
source('aggregate_table.R')
source('map.R')
source('bargraph.R')
source('PieChart.R')
```
---
### Introduction:
Food accessibility has become a major concern for people during the pandemic,
even more so than ever before. Due to rising unemployment and public regulation
policies, the stability people may have experienced previously with food has
undoubtedly changed. We wanted to investigate the relationship between COVID-19,
the number of operating restaurants, and emergency food resources, to discover
how much of an effect the pandemic has had on people’s ability to access food,
specifically in King County. This will give us a better understanding of the
situation, which can help both our own communities as well as others moving forward.

---
Summary Information:



```{r echo = F}
library(knitr)
kable(combined_data, 
      caption = "**King County Municipalities Emergency Food Sources
      & Covid Data**",
      col.names = c("City", 
                    "Number of Food Sources", 
                    "Positives", 
                    "Deaths", 
                    "Deaths per Food Source", 
                    "Positives per Food Source"),
      align = "lccccc") 
```

```{r echo = F}
bar_graph
```


```{r echo = F}
deaths_per_fs_map
```

The municipality in King County with the highest concentration of COVID deaths
to number of food sources seems to be the city of `r max_deaths_per_fs_city`.
(Elaborate more.....)


The pie chart represents a breakdown of the different communities being served at various operating emergency food resources during the COVID-19 pandemic. As we can see, among the five major communities being served, about `r youth_percent`% serves the Youth community, `r public_percent`% serves the general public community, `r older_percent`% serves the elderly community, `r students_percent`% serves the students community, `r other_percent`% serves the other community.

This visualization revealed that the elderly community is one of the most undeserved communities during the pandemic, which is alarming considering that this community is also one of the most vulnerable.